An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
change vector db range filter

	Vector databases also show relatively poor performance on range queries. Among them, Milvus performs better than the others, even surpassing ACORN under high recall settings. PASE performs poorly on small-range queries, with recall lower than 0.1, so it does not appear in Figure~\ref{fig:exp_8_2}. VPASE also performs better on large-range queries, but compared to PASE, its performance on small ranges is significantly better, achieving higher recall despite very low QPS.

>>>>

	Vector databases also show relatively poor performance on range queries. Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings. PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy. VBASE performs better on large-range queries. Compared to PASE, its performance on small ranges is significantly improved, achieving higher recall despite very low QPS.
